Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-02 paper/paper.tex
Slight changes to immunopathology sentence to make it better

It remains unclear why only some infected cells trigger innate-immune responses.
Two possible contributors are pure stochasticity and pre-existing variation in cellular state.
For instance, only some cells induce IFN even upon homogeneous treatment with synthetic innate-immune ligands~\citep{shalek2013single, shalek2014single, wimmers2018single}, and there is evidence that the frequency of IFN induction depends on a cell's pre-existing chromatin state~\citep{bhushal2017cell}.
Consistent with these observations, despite the beneficial antiviral effects of IFN signaling, these effects can come at a significant cost due to increased immunopathology and therefore host-cell intrinsic limitation of the IFN response would help to limit the damage done by this inflammatory process~\citep{iwasaki2014innate}.
But for influenza, a third possible contributor also looms large: viral genetic diversity.
Specifically, because influenza has a high mutation rate, even if the \emph{consensus} sequence of a viral population is ``wildtype,'' individual virions will often have genetic defects~\citep{parvin1986measurement, suarez1992heterogeneity, suarez1994estimation, bloom2014experimentally, pauly2017novel}.
Indeed, many studies have identified mutations that increase IFN induction when engineered into a viral population~\citep{velthuis2018mini, du2018genome, killip2017single, perez2014unbiased}, and more IFN is induced by viral stocks that contain defective virions with internal deletions in the polymerase genes~\citep{baum2010preference, tapia2013defective, boergeling2015evidence, dimmock2015cloned}.

>>>>

It remains unclear why only some infected cells trigger innate-immune responses.
Two possible contributors are pure stochasticity and pre-existing variation in cellular state.
For instance, only some cells induce IFN even upon homogeneous treatment with synthetic innate-immune ligands~\citep{shalek2013single, shalek2014single, wimmers2018single}, and there is evidence that the frequency of IFN induction depends on a cell's pre-existing chromatin state~\citep{bhushal2017cell}.
Such self-imposed limitation of an IFN response is consistent with the biological impact of IFN as, despite the beneficial antiviral effects of IFN signaling, these effects can come at a significant cost due to increased immunopathology~\citep{iwasaki2014innate}.
But for influenza, a third possible contributor also looms large: viral genetic diversity.
Specifically, because influenza has a high mutation rate, even if the \emph{consensus} sequence of a viral population is ``wildtype,'' individual virions will often have genetic defects~\citep{parvin1986measurement, suarez1992heterogeneity, suarez1994estimation, bloom2014experimentally, pauly2017novel}.
Indeed, many studies have identified mutations that increase IFN induction when engineered into a viral population~\citep{velthuis2018mini, du2018genome, killip2017single, perez2014unbiased}, and more IFN is induced by viral stocks that contain defective virions with internal deletions in the polymerase genes~\citep{baum2010preference, tapia2013defective, boergeling2015evidence, dimmock2015cloned}.
